Response to reviewers

### 2022-02-03 paper/paper.Rmd
Edited the paper and add the response.

According to @WickhamHadley2014TD, tidy data sets comply with three rules: (i) each variable forms a column, (ii) each observation forms a row, and (iii) each type of observational unit forms a table. The raw data does not comply with these rules, thus we re-arrange and wrangle the data into tidy data form, columns corresponding to individual ID, year, job number, wage in dollars and the demographic variables.<!-- AE comment: This sentence is unclear. What is dplyr used for? Are there tidyverse packages used but not mentioned? If not, splitting this sentence into two may make it clearer which package is used to what purpose. Also, I haven't tried it in code, but I imagine that the data could be tidied as described just using pivot_longer, at least for the job number, year, and wage data. In other words, I don't see why dplyr or stringr would be needed for the data described on page 6.--> This is done using the `tidyverse` suite of packages [@tidyverse], `tidyr` [@tidyr] to pivot the data into long form, `dplyr` [@dplyr], and `stringr` [@stringr] for creating new variables, and levels of factors by text wrangling. The long form of the data makes it possible to do these data transformations efficiently, and it is an intermediate step towards the final target data. The code for tidying the data are demonstrated at \url{`r yowie_pkgdown`/articles/raw-to-input-data.html} but also described in the subsequent subsections.

@@

The number of jobs (`number_of_jobs`) for each respondent per year is computed from the number of non-missing values of hourly wage *and* hours worked. If either the hourly wage or hours worked is missing, we do not tally this. <!-- AE comment: "If either the hourly wage or hours worked is missing, we do not tally this." I take "this" to mean "number_of_jobs". But in row 2, total_hours is missing, yet number_of_jobs is 1. The number of jobs (1) was tallied even though hours worked was missing. -->

@@

<!--The next paragraph, which begins “The anomalies are also found” should perhaps be “Similar anomalies were found.” Was it the same respondents with the extremely high wages that showed extremely high number of hours of work? I suspect not, but please be explicit.-->
<!--AE comment: Rewrite this sentence. "Observations" aren't working 420 hours. A "respondent" might have been reported as having worked 420 hours per week.--> The anomalies are also found in the total hours of work, where some observations reported as having worked for 420 hours a week in total. 
According to @MichaelRPergamit2001DWTN, one of the flaws of the NLSY79 employment data is that the NLSY79 collects the information of the working hours since the last interview. Thus, it might be challenging for the respondents to track the within-job hours' changes between survey years, especially for the respondents with fluctuating working hours or seasonal jobs. It even has been more challenging since 1994, after which respondents were only surveyed every other year and thus had to recall two full years’ job history. This shortcoming might also contribute to the fluctuation of one's wages data.

@@

```{r compare_xp_to_yrworkforce, fig.cap = "The association between the lenght of time in the workforce (years) and the work experience. The color represents the respondents (id). Generally, the longer someone were in the workforce, the higher the work experience. However, some of the respondents have much lower working experience compared their duration in the workforce."}
```

>>>>

According to @WickhamHadley2014TD, tidy data sets comply with three rules: (i) each variable forms a column, (ii) each observation forms a row, and (iii) each type of observational unit forms a table. The raw data does not comply with these rules, thus we re-arrange and wrangle the data into tidy data form, columns corresponding to individual ID, year, job number, wage in dollars and the demographic variables.This is done using the `tidyverse` suite of packages [@tidyverse], i.e., `tidyr` [@tidyr] to pivot the data into long form, `dplyr` [@dplyr] and `stringr` [@stringr] to create new variables from the downloaded data from the database, and create levels of factors by text wrangling. The long form of the data makes it possible to do these data transformations efficiently, and it is an intermediate step towards the final target data. The code for tidying the data are demonstrated at \url{`r yowie_pkgdown`/articles/raw-to-input-data.html} but also described in the subsequent subsections.

@@

The number of jobs (`number_of_jobs`) for each respondent per year is computed from the number of non-missing values of hourly wage. Even if the information of hours worked exists for a particular observation, we do not tally when the hourly wage is missing.

@@

<!--The next paragraph, which begins “The anomalies are also found” should perhaps be “Similar anomalies were found.” Was it the same respondents with the extremely high wages that showed extremely high number of hours of work? I suspect not, but please be explicit.-->
The anomalies are also found in the total hours of work, where some observations reported as having worked for 420 hours a week in total. According to @MichaelRPergamit2001DWTN, one of the flaws of the NLSY79 employment data is that the NLSY79 collects the information of the working hours since the last interview. Thus, it might be challenging for the respondents to track the within-job hours' changes between survey years, especially for the respondents with fluctuating working hours or seasonal jobs. It even has been more challenging since 1994, after which respondents were only surveyed every other year and thus had to recall two full years’ job history. This shortcoming might also contribute to the fluctuation of one's wages data.

@@

```{r compare_xp_to_yrworkforce, fig.cap = "The association between the lenght of time in the workforce and the work experience. The color represents the respondents. Generally, the longer someone were in the workforce, the higher the work experience. However, some of the respondents have much lower working experience compared their duration in the workforce.", eval=FALSE}
```

### 2022-02-03 response/response1.Rmd
Edited the paper and add the response.

>>>>

\begin{description}
\item[Reviewer 1:]\textcolor{violet}{It's unclear from context what is being referred to from the Huebner et al 2020 citation.}
\end{description}

* We have fixed the sentences and the reference.

\begin{description}
\item[Reviewer 1:]\textcolor{violet}{What is dplyr used for? Are there tidyverse packages used but not mentioned? If not, splitting this sentence into two may make it clearer which package is used to what purpose. Also, I haven't tried it in code, but I imagine that the data could be tidied as described just using pivot_longer, at least for the job number, year, and wage data. In other words, I don't see why dplyr or stringr would be needed for the data described on page 6.}
\end{description}

* We have split the sentences and described the use of each package mentioned.

\begin{description}
\item[Reviewer 1:]\textcolor{violet}{please clarify. "If either the hourly wage or hours worked is missing, we do not tally this." I take "this" to mean "number_of_jobs". But in row 2, total_hours is missing, yet number_of_jobs is 1. The number of jobs (1) was tallied even though hours worked was missing.}
\end{description}

* We have clarified this that we only tally the number of jobs if the hourly wage is not missing.

\begin{description}
\item[Reviewer 1:]{"to find the anomaly in the wages values" This comes as a surprise to the reader. What anomaly? The wage anomalies should be mentioned in the introduction so as not to be a surprise at this point in the manuscript.}
\end{description}
